Who will win the US 2024 election?!!

### 2024-03-15 paper/paper.qmd
Abstract updated and github link added

---
title: "Who will win the US 2024 election?!!"
author:
  - Monica Sainani
  - Kaavya Kalani
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "This study investigates the dynamics of voting behaviour during the US presidential election in 2022 using
 data from the American Community Survey(ACS) 2022 sample.

 We look at the correlation between voting preferences and demographic, socioeconomic, and geographic factors,
 such as age, income, education, state of residency, and gender.

 Our study reveals complex trends and determinants of voting behaviour, providing understanding into the complex
 relationships between personal traits and local factors that influence election results.

 This research contributes to a better understanding of the factors influencing political engagement in American
 democracy by offering insightful information that might guide future electoral strategies and policy discussion."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

## Introduction to the Variables
These are the key variables utilized in our statistical analysis of voting behavior during the 2022 presidential
election. These variables are drawn from the American Community Survey (ACS) 2022 sample and encompass demographic,
socio-economic, and geographic characteristics that may influence individuals' voting preferences.

>>>>

---
title: "Who will win the US 2024 election?!!"
author:
  - Monica Sainani
  - Kaavya Kalani
thanks: "Code and data supporting this analysis is available at: https://github.com/sainanim/Predictions-for-the-US-2024-Elections"
date: today
date-format: long
abstract: "This study investigates the dynamics of voting behaviour of americans leveraging demographic, socioeconomic, and geographic factors, such as age, family income, education, state of residency, and sex. We use a Bayesian Logistic Regression model with Post-Stratification to predict the outcome between Biden and Trump with the mentioned factors as predictors. Our study indictates that Biden is likely to be re-elected as the president with a 10% lead. This research contributes to a better understanding of the factors influencing political engagement in American democracy by offering insightful information that might guide future electoral strategies and policy discussion."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

## Introduction to the Variables
These are the key variables utilized in our statistical analysis of voting behavior during the 2022 survey.
These variables are drawn from the American Community Survey (ACS) 2022 sample and encompass demographic,
socio-economic, and geographic characteristics that may influence individuals' voting preferences.
